---
title: "Analyze Tone Perception (1 syllable)"

output: html_notebook
---
### Goals
This study aims to examine the range of variation in acceptable pronunciation of Mandarin tones. 

* Identify perceptual boundaries between tones
  * Determine the range of variation between native listeners
  * Compare the range of variation between types of syllables with the variation from individual listeners
* Create a model to predict the probabilities of a stimulus being identified as each tone  

### Related Work
Bei Yang's PhD thesis

### Procedure
6 native speakers of Mandarin listened to single syllables with varying frequency shifts and were shown 4 words with the same phoneme as the stimulus that varied only in tone. Subjects indicated which word, if any, they heard. Each stimulus could be heard up to two times. Syllables were synthesized using samples of a native female speaker from Beijing. The range of the speaker's voice was divided into 7 points, equally spaced on a semitone scale. 10 carrier syllables were used (e.g. */ma*, */yi*). For each carrier syllable, 49 stimuli were generated by linearly varying the fundamental frequency between every combination of start and end points. The evaluation was done from a webpage and consisted of 10 sections. Each section presented the 49 synthesized stimuli for a single carrier syllable in random order. To prevent fatigue, subjects were able to stop the test after each section and return to it at a later time.

### Analysis

Load the data and look at it. Start and end frequencies (*start.freq*, *end.freq*) are coded on a semitone scale from -6 to 6. This emcompasses the usual range of the speaker's voice. *freq.shift* is the amount of change betwewen *start.freq* and *end.freq*. For example -12 is down by 12 semitones.

Tones are referred to as T1, T2, T3, T4. Note that T3 is selected far less frequently than the others. This is not surprising because none of the stimuli have the "V" shape typical of T3 in isolation. A follow-up study is probably necessary to investigate the boundaries of for the V-shaped T3.

T1, T2, and T4 have pretty even proportions of selection. 
```{r}
library("tidyverse") #alwways
source("../utils/dataWrangling.R") #helper functions to load data

subjects <- c("s29", "s30", "s31", "s32", "s33", "s34")
master <- get_results(subjects, "../data/singleSyllableVariedTonePerception/")

summary(master)
```

Let's plot the data from one subject for group of stimuli. TN is "none of the above". T2 is the rising tone and occupies top left region (end.freq > start.freq). Tone 4 falls and occupies the bottom right region (end.freq < start.freq). T1 is normally described as "high steady." We would expect to find it along the diagonal on the top right corner. From these 4 plots, tone movements up to 2 semitones in either direction still get perceived as tone 1. Without the contrast from adjacent utterances, low steady tones also get perceived as tone 1.
```{r}
library("gridExtra")

# Custome palette that assigns a specific color to each tone
palette <- c(
  "T1" = "skyblue",
  "T2" = "lightcoral", 
  "T3" = "lightgreen", 
  "T4" = "gold3",
  "TN" = "slategray" 
)

# Function that filters the results of one subject for one carrier syllable
# and plots it in a grid
plot_one_group <- function(data, my_subject, my_syllable) {
  d <- filter(data, subject == my_subject & carrier_syllable == my_syllable)
       
  ggplot(d) +
    xlab("Start frequency (ST)") + ylab("End Frequency (ST)") +
    scale_x_continuous(breaks = seq(-6, 6, by = 2)) +
    scale_y_continuous(breaks = seq(-6, 6, by = 2)) +
    geom_label(aes(x=start.freq, y=end.freq, color=selected_tone, label=selected_tone), show.legend = FALSE) +
    scale_color_manual(values = palette,
                       limits = names(palette)) +
    labs(title = paste("Subject: ", my_subject, ", Syllable: ", my_syllable, sep=""))
}

ma29 <- plot_one_group(master, "s29", "ma")
mao29 <- plot_one_group(master, "s29", "mao")

ma32 <- plot_one_group(master, "s32", "ma")
mao32 <- plot_one_group(master, "s32", "mao")

grid.arrange(ma29, mao29, ma32, mao32, nrow=2)
```


## 