---
title: "Compare Gestures III.1: February 2020 pilot data"
output: html_notebook
---

# Reference Data

Load pitch and intensity info for the ref phrases:

```{r, message=FALSE, warn=FALSE}
library("zoo")
library("rPraat")
library("tidyverse")

path="../data/21_02-study/reference/"
ref_freq <- 116.54

# Find intensity files
setwd(paste0(path, "_intensity"))
it_filenames <- dir(pattern="\\.IntensityTier$")

# Find pitchTier files 
setwd("../_pitchtier")
pt_filenames <- dir(pattern="\\.PitchTier$")

# Find Prosogram PitchTier files
setwd("../_prosogram_pt")
psg_filenames <- dir(pattern="\\.PitchTier$")

# Interpolate pitch and intensity for one phrase and plot
setwd("../../../../notebooks/")

# A vector with all the phrases
ref_phrases <- do.call("rbind", lapply(pt_filenames, function(elt) {
  str_split(elt, '.PitchTier')[[1]][1]
}))[,1]

#All the ref pitchtiers, not interpolated
ref_pts <- lapply(pt_filenames, function(elt) {
  my_pt<-pt.read(paste0(path, "_pitchtier/", elt))
})

# Put all the reference pitch tiers into a list
ref_pts_interp <- lapply(pt_filenames, function(elt) {
  my_pt<-pt.read(paste0(path, "_pitchtier/", elt))
  interpolated <- pt.interpolate(my_pt, seq(0, my_pt$tmax, by=0.01))
  interpolated$f <- hertz_to_semitones(interpolated$f, ref_freq)
  interpolated
})

# All the ref prosograms, not interpolated
ref_psgs <- lapply(psg_filenames, function(elt) {
  my_pt<-pt.read(paste0(path, "_prosogram_pt/", elt))
})

# Put all the Prosogram pitch tiers into a list
ref_psgs_interp <- lapply(psg_filenames, function(elt) {
  my_pt<-pt.read(paste0(path, "_prosogram_pt/", elt))
  interpolated <- pt.interpolate(my_pt, seq(0, my_pt$tmax, by=0.01))
  interpolated$f <- hertz_to_semitones(interpolated$f,ref_freq)
  interpolated
})

# Non-interpolated intensity tiers
ref_its <- lapply(it_filenames, function(elt) {
  my_it <- it.read(paste0(path, "_intensity/", elt))
})

# Put all the reference intensity tiers into a list
ref_its_interp <- lapply(it_filenames, function(elt) {
  my_it <- it.read(paste0(path, "_intensity/", elt))
  it.interpolate(my_it, seq(0, my_it$tmax, by=0.01))
})

# Get the times of each phrase
ref_times <- do.call("rbind", lapply(ref_pts_interp, function(elt) {
  elt$tmax
}))[,1]

# A tibble containing each phrase and its duration
ref_info <- tibble(phrase=ref_phrases, duration=ref_times)

```

Some helper functions to get duration, time stamps, interpolated f0 (stylized or not) values, interpolated intensity values given the phrase name:

```{r}

# Gets the interpolated prosogram object
get_ref_psgs_interp <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_psgs_interp[[index]])
}

# A function that gets the duration given the phrase name
get_ref_duration <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_info$duration[index])
}

# Get the times stamps for interpolation given the phrase name
get_ref_timestamps <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_pts_interp[[index]]$t)
}

# Get the interpolated frequency values given the phrase name
# (frequency time series)
get_ref_tsf <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_pts_interp[[index]]$f)
}

# Get the interpolated prosogram frequency values given the phrase name
# (prosogram frequency time series)
get_ref_ptsf <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_psgs_interp[[index]]$f)
}

# Get the interpolated intensity values given the phrase name
# (intensity time series)
get_ref_tsi <-function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_its_interp[[index]]$i)
}
```


Compare the Pearson's Correlation values between Praat and Prosogoram frequency curves

```{r}
library("wCorr") # for the weighted correlation function

# Helper function to find the straight up correlation between the praat and prosogram frequency curves
get_corr_praat_psg <- function(gest_name) {
  praat_pitch <- get_ref_tsf(gest_name)
  prosogram_pitch <- get_ref_ptsf(gest_name)
  return(cor(praat_pitch, prosogram_pitch, method="pearson"))
}

corr_praat_psg_refs <- do.call("rbind", lapply(ref_phrases, function(elt) {
  get_corr_praat_psg(elt)
}))[,1]

# Helper function to find the weighted correlation between the praat and prosogram frequency curves
get_weighted_corr_praat_psg <- function(phrase_name) {
  praat_pitch <- get_ref_tsf(phrase_name)
  prosogram_pitch <- get_ref_ptsf(phrase_name)
  intensity <- get_ref_tsi(phrase_name)
  
  wc <- weightedCorr(praat_pitch, prosogram_pitch, method = "Pearson", 
               weights = intensity, ML = FALSE, fast = TRUE)
  return(wc)
}

get_rmse_praat_psg <- function(phrase_name) {
  praat_pitch <- get_ref_tsf(phrase_name)
  prosogram_pitch <- get_ref_ptsf(phrase_name)
  intensity <- get_ref_tsi(phrase_name)
  
  r <- rmse(preds=praat_pitch, actuals=prosogram_pitch, weights=intensity)
  return(r)
}

wcorr_praat_psg_refs <- do.call("rbind", lapply(ref_phrases, function(elt) {
  get_weighted_corr_praat_psg(elt)
}))[,1]

rmse_praat_psg_refs <- do.call("rbind", lapply(ref_phrases, function(elt) {
  get_rmse_praat_psg(elt)
}))[,1]

results_wcorr_praat_prosogram <- tibble(phrase=ref_phrases, corr.praat.psg=corr_praat_psg_refs,
                                        wcorr.praat.psg=wcorr_praat_psg_refs)
print(as.matrix(results_wcorr_praat_prosogram), quote = FALSE)

```
All of these values are quite high.


Compare Prosograms between pairs of phrases
```{r}

pbis <- c(2, 4, 6, 8, 10, 12)
#ref_pairs<-tibble(pid=pbis-1,phrase=ref_phrases[pbis-1], pid_bis=pbis, phrase_bis=ref_phrases[pbis])

psg_pairs_interp<-do.call("rbind", lapply(pbis, function(id) { 
  psg1<-ref_psgs[id]
  psg2<-ref_psgs[id-1]
  tmax <- max(psg1[[1]]$tmax, psg2[[1]]$tmax)
  len_to_interp <- seq(0, tmax, by=0.01) %>% length()
  psg1_interp<-pt.interpolate(psg1[[1]], seq(0, psg1[[1]]$tmax, length=len_to_interp))
  psg2_interp<-pt.interpolate(psg2[[1]], seq(0, psg2[[1]]$tmax, length=len_to_interp))
  
  it1<-ref_its[id]
  it1_interp<-it.interpolate(it1[[1]], seq(0, it1[[1]]$tmax, length=len_to_interp))
  
  f1<- hertz_to_semitones(psg1_interp$f, ref_freq)
  f2<- hertz_to_semitones(psg2_interp$f, ref_freq)
  
  my_corr<-weightedCorr(f1, f2, method = "Pearson", 
               weights = it1_interp$i, ML = FALSE, fast = TRUE)
  my_rmse<-rmse(preds=f1, actuals=f2, weights=it1_interp$i)
  tibble(pid=id, corr=my_corr, rmse=my_rmse)
  return(tibble(pid=id, corr=my_corr, rmse=my_rmse))
}))
  
  
d1<-tibble(f1=psg1_interp$f, t1=psg1_interp$t, f2=psg2_interp$f, t2=psg2_interp$t)
     ggplot(data=d1, aes(x=t1, y=f1)) +
      geom_line(aes(color="pitch1")) +
      scale_color_discrete(name = "Data")  +
      geom_line(aes(x=t1, y=f2, color="pitch2"))
      
mean(psg_pairs_interp$corr) #.508
sd(psg_pairs_interp$corr) #.379

mean(psg_pairs_interp$rmse) # 4.473
sd(psg_pairs_interp$rmse) #.91
         
#Between prosograms of phrase pairs, correlation ranges from -0.175 to 0.895 (mean .508, SD .379) and RMSE ranges from 3.77 to 6.10 (mean 4.473, sd .91)

#mean correlation is .508 (min:-.175, max: .895, SD; 0.379), and mean RMSE is 4.473 (m)
```




Let's plot the graphs with the lowest correlation value:

```{r}
plot_ref_curves <- function(phrase_name) {
  # first get the info
  praat_pitch <- get_ref_tsf(phrase_name)
  prosogram_pitch <- get_ref_ptsf(phrase_name)
  intensity <- get_ref_tsi(phrase_name)
  timestamps <- get_ref_timestamps(phrase_name)
  
  # combine into a tibble
  ref_data <- tibble(f=praat_pitch, i=intensity, psg.f=prosogram_pitch, t=timestamps)
  
  # plot
  ggplot(data=ref_data, aes(x=t, y=f)) +
      geom_line(aes(color="Praat Pitch")) +
      scale_color_discrete(name = "Data")  +
      geom_line(aes(x=t, y=i, color="Intensity")) +
      geom_line(aes(x=t, y=psg.f, color="Prosogram Pitch")) +
      labs(title="Interpolated pitch tier and intensity tiers", subtitle=paste("Phrase:",phrase_name),
          x="time (seconds)",
          y="Frequency (Hz) for pitch, \nunspecified for intensity")  
}
```

These two curves had the lowest correlation: 0.87

```{r, fig.keep='all'}
plot_ref_curves(ref_phrases[1])
```

# Comparing Gestures

```{r}
library("jsonlite")
library("timetk")

# Get all the filenames of the gestures
path="../data/21_02-study/all_gestures/"
setwd(path)
gest_filenames <- dir(pattern="\\.gest$")
name <- gest_filenames[1]

# Extract the reference phrase from the whole gesture name
get_ref_name <- function(gest_name) {
  return(str_split(gest_name, '-')[[1]][3])
}

# Finds the number of samples in the reference for the particular gesture
get_num_samples <-function(gest_name) {
# Find how many samples are in the ref file
  ref_phrase <- get_ref_name(gest_name)  
  return(length(get_ref_timestamps(ref_phrase)))
}

# Load gest data and convert time
prep_gest<-function(gest) {
  # Convert time to percentage
  max_time <- tail(gest$t_end, 1)
  gest <- gest %>% mutate(percent=t_init/max_time) %>%
             # only keep local scrub time and the freq values 
             select(percent, f, scrub)
  return(gest)
}

# args: data - tibble with columns: percent (% of way through signal) & f (frequency at that point), 
# num_samples - # equally spaced points in outpt
# returns: tibble with coluumns index & value. index has num_samples equally spaced points from 0 to 1
# values are interplolated from f
get_interpolated_data <- function(data, num_samples) {
  # Add end points at 0 and 1 if they don't already exist, duplicating first and last available f value
  if (! 0 %in% data$percent) {
    data <- add_row(data, percent=0, f=data$f[1], scrub=data$scrub[1], .before=1)
  }
  if (! (1 %in% data$percent)) {
    data <- add_row(data, percent=1, f=tail(data$f, 1), scrub=tail(data$scrub, 1))
  }
          
  # Create a tibble with all the points we are interested in, with NA values
  sample_points <- tibble(percent=seq(0, 1, length.out=num_samples), f=NA, scrub=NA) 
  
  # Add all the sample points whose scrub value doesn't already exist in data
  data2 <- bind_rows(data, filter(sample_points, !(percent %in% data$percent)))  %>%
    # Then sort by scrub columns  
    arrange(percent)
  
  # Transform into zoo object to fill the NAs with interpolated values
  z <- read.zoo(data2) %>% na.approx %>%
   tk_tbl(preserve_index=TRUE, rename_index="index") %>%
   filter(index %in% sample_points$percent)
  
  return(z)
}

setwd("../../../notebooks/")

# A vector with just the names of the phrases (w/o .json extension)
gests <- do.call("rbind", lapply(gest_filenames, function(elt) {
  str_split(elt, '.gest')[[1]][1]
}))[,1]

# Original gestures
gest_originals <- lapply(gest_filenames, function(elt) {
  result <- fromJSON(paste0(path, elt)) %>% as_tibble() %>% 
  # NOTE THIS EXTRA STEP      
  prep_gest()
})

# Returns the index of the gesture
get_gest_index <- function(gest_name) {
  index <- match(gest_name, gests)
  if (is.na(index)) { return(NULL) }
  return(index)
}

# Interpolated time series data of f & scrub value
gest_interps <- lapply(gests, function(elt) {
  # Elt is the name of a gesture. We want to find its index first
  index<-get_gest_index(elt)
  
  # In order to get the actual gesture data
  gest_orig<-gest_originals[[index]]
  
  # Gets number of samples for the gest, which is computed from the reference
  num_samples<-get_num_samples(elt)
  
  # Do the interpolation  
  gest_interp<-get_interpolated_data(gest_orig, num_samples)
  
  return(gest_interp)
})

```

Organize gestures into a Tibble

```{r}
gests_data <- do.call("rbind", lapply(gests, function(elt) {
  parts<-str_split(elt, '-')[[1]]
  ref_phrase <- parts[3]
  phrase_id <- str_split(ref_phrase, '_')[[1]][1]
  tibble(phrase=ref_phrase, pid=phrase_id, type=parts[2], subject=parts[4], order=parts[1], gest_name=elt)
})) %>% mutate(id = row_number()) %>%
  select(subject, type, pid, order,gest_name, phrase, id)
```

Let's compute some stuff and add to the tibble
```{r}

# Compute the correlation and rms given the entire gesture name
get_corr <- function(gest_name, weights=FALSE) {
  # Get the index of the gesture
  index<-get_gest_index(gest_name)
  # Use it to get the freq of the gesture
  gest_pitch <- gest_interps[[index]]$f
  
  # Get the reference phrase
  phrase_name <- get_ref_name(gest_name)    
  # Use it to get the prosogram pitch ref and the intensity
  prosogram_pitch <- get_ref_ptsf(phrase_name)
  
  # If using weights, get the intensity of the ref phrase
  if (weights) {  
    intensity <- get_ref_tsi(phrase_name)
  
    wc <- weightedCorr(gest_pitch, prosogram_pitch, method = "Pearson", 
               weights = intensity, ML = FALSE, fast = TRUE)
    return(wc)
  } else {
    return(weightedCorr(gest_pitch, prosogram_pitch, method = "Pearson", 
               weights = rep(1, length(gest_pitch)), ML = FALSE, fast = TRUE))
  }
}

wcorr_all <- do.call("rbind", lapply(gests, function(elt) {
  get_corr(elt, weights=TRUE)
}))[,1]

gests_data <- add_column(gests_data, wcorr=wcorr_all)
```


Make some filtering functions:

```{r}
get_gests_by_subject <- function(s, t) {
  if (missing(s) & missing(t)) {
    return(gests_data %>% filter(subject==subject, type==type))
  } else if (missing(s)) {
    return(gests_data %>% filter(subject==subject, type==t))
  } else if (missing(t)) {
    return(gests_data %>% filter(subject==s, type==type))
  }
  return(gests_data %>% filter(subject==s, type==t))
}

get_gests_by_phrase <- function(p_id, t) {
  if (missing(p_id) & missing(t)) {
    return(gests_data %>% filter(pid==pid, type==type))
  } else if (missing(p_id)) {
    return(gests_data %>% filter(pid==pid, type==t))
  } else if (missing(t)) {
    return(gests_data %>% filter(pid==p_id, type==type))
  }
  return(gests_data %>% filter(pid==p_id, type==t))
}

```


By phrase

```{r}
# Get the unique pids
p_ids <- c('2', '2bis', '7', '7bis', '8', '8bis', '10', '10bis', '11', '11bis', '21', '21bis')

wcorr_p_blind <- do.call("rbind", lapply(p_ids, function(elt) {
  mean(get_gests_by_phrase(p_id=elt, t='blind')$wcorr)
}))[,1]

wcorr_p_guide <- do.call("rbind", lapply(p_ids, function(elt) {
  mean(get_gests_by_phrase(p_id=elt, t='guide')$wcorr)
}))[,1]

wcorr_by_pid <- tibble(pid = p_ids, wcorr_blind = wcorr_p_blind, wcorr_guide = wcorr_p_guide) %>%
                arrange(pid)

```



```{r}
# Boxplots of wcorr by phrase
gests_data %>%
  ggplot(aes(x=pid, y=wcorr, fill=factor(type))) +
  geom_boxplot() +
  labs(title="Correlation of gesture with reference", 
            subtitle="Grouped by phrase",
            x="Phrase id")
```


```{r}
# Boxplots of wcorr by subject
gests_data %>%
  ggplot(aes(x=subject, y=wcorr, fill=factor(type))) +
  geom_boxplot() +
  labs(title="Correlation of gesture with reference", 
            subtitle="Grouped by subject",
            x="Subject id")
```


```{r}
plot_gest_and_ref <- function(gest_name) {
  # Get the index of the gesture
  index<-get_gest_index(gest_name)
  # Use it to get the freq of the gesture
  gest_pitch <- gest_interps[[index]]$f
  
  # Get the reference phrase
  phrase_name <- get_ref_name(gest_name)    
  # Use it to get the prosogram pitch ref and the intensity
  prosogram_pitch <- get_ref_ptsf(phrase_name)
  intensity <- get_ref_tsi(phrase_name)
  
  wcorr <- slice(gests_data, index)$wcorr
  
  my_data <- tibble(gest=gest_pitch, ref=prosogram_pitch, i=intensity, 
                    percent=gest_interps[[index]]$index)
  
  my_plot <- ggplot(data=my_data, aes(x=percent, y=gest, color="gesture")) +
    scale_color_discrete(name = "Data source") +
    geom_line() +
    geom_line(data=my_data, aes(x=percent, y=ref, color="reference")) +
    geom_line(data=my_data, aes(x=percent, y=i, color="intensity")) +
    labs(title=paste(gest_name, "with its reference"), 
            subtitle=paste("Weighted Correlation:", wcorr),
            y="frequency (semitones from 130hz) \nunspecified for intensity",
            x="percent time")
  return(my_plot)
}

plot_gest_and_ref(gests[2])

```

This plot shows a big problem with how we are comparing the gesture with the reference. In the reference phrase, there is no sound at the beginning and end of the recording. If we look at the intensity plot, the vocalization does not start right at 0 and end right at 1. The gesture, starts at the point where sound starts. We have been comparing the gesture with the entire duration of the reference, but we should really only be comparing it with the central part of the recording with the actual sound.

This might be why results so far have not made sense.

# A different way of comparing

Compare the gesture to only the part of the reference with the syllables. 

```{r}

compare2 <- function(gest_id) {
  # Get the first gesture from the list
  my_gest <- slice(gests_data, gest_id)  
  
  # Get the original data 
  my_gest_data <- gest_originals[[gest_id]]
  # Find the starting and ending scrub times
  start_scrub <- my_gest_data$scrub[1]
  end_scrub <- tail(my_gest_data$scrub, 1)

  # Find the corresponding phrase for this gesture
  my_ref <- get_ref_psgs_interp(my_gest$phrase)
  # Number of points in my_ref
  my_ref_length <- length(my_ref$f)
  # Get the start and index of the reference phrase based on the start and end scrub points
  my_ref_start_index <- floor(start_scrub * my_ref_length)
  my_ref_end_index <- ceiling(end_scrub * my_ref_length)
  # Get the part of the reference to compare with the gesture
  my_ref_f <- my_ref$f[my_ref_start_index:my_ref_end_index]
  my_ref_t <- my_ref$t[my_ref_start_index:my_ref_end_index]
  
  # Get the intensity too
  my_ref_i <- get_ref_tsi(my_gest$phrase)[my_ref_start_index:my_ref_end_index]
  
  # Now, interpolate the original gesture based on the number of points in the subset of the reference
  my_gest_interp<-get_interpolated_data(my_gest_data, length(my_ref_f))

  
  return(weightedCorr(my_ref_f, my_gest_interp$f, method = "Pearson", 
                      weights = my_ref_i, ML = FALSE, fast = TRUE))
}

# Run new comparison on all the gestures
compare2_all <- do.call("rbind", lapply(gests_data$id, function(elt) {
  compare2(elt)
}))[,1]

gests_data <- add_column(gests_data, wcorr2 = compare2_all)
```




```{r}
gests_data %>%
  ggplot(aes(x=pid, y=wcorr2, fill=factor(type))) +
  geom_boxplot() +
  labs(title="Correlation of gesture with reference", 
            subtitle="Grouped by phrase",
            x="Phrase id")
```

```{r}

# Boxplots of wcorr by subject
gests_data %>%
  ggplot(aes(x=subject, y=wcorr2, fill=factor(type))) +
  geom_boxplot() +
  labs(title="Correlation of gesture with reference", 
            subtitle="Grouped by subject",
            x="Subject id", y="Correlation score")
```




```{r}
# Put the original and the gesture into a tibble
  # comparison<-tibble(ref_f = my_ref_subset, ref_t = my_ref_subset_t, ref_i = my_refi_subset,
  #                  gest_f = my_gest_interp$f, gest_s = my_gest_interp$scrub)

#
# ggplot(data=comparison, aes(x=ref_t, y=ref_f)) +
#     scale_color_discrete(name = "Data source") +
#     geom_line(data=comparison, aes(x=ref_t, y=gest_f, color="gesture")) +
#     geom_line(data=comparison, aes(x=ref_t, y=ref_f, color="reference"))

```

