---
title: "Compare Gestures III.2: February 2020 pilot data"
output: html_notebook
---

Starts by copying the important parts of 8_compareGesturesPilot and continues the analysis

```{r}
options("scipen"=100, "digits"=4)
options(scipen=999)
options(pillar.sigfig = 5)
```


# 1. Reference Data

```{r, message=FALSE, warn=FALSE}
library("zoo")
library("rPraat")
library("tidyverse")
library("wCorr") # for the weighted correlation function
library("scales")

path="../data/21_02-study/reference/"
ref_freq <- 116.54

# Find intensity files
setwd(paste0(path, "_intensity"))
it_filenames <- dir(pattern="\\.IntensityTier$")

# Find pitchTier files 
setwd("../_pitchtier")
pt_filenames <- dir(pattern="\\.PitchTier$")

# Find Prosogram PitchTier files
setwd("../_prosogram_pt")
psg_filenames <- dir(pattern="\\.PitchTier$")

# Interpolate pitch and intensity for one phrase and plot
setwd("../../../../notebooks/")

# A vector with all the phrases
ref_phrases <- do.call("rbind", lapply(pt_filenames, function(elt) {
  str_split(elt, '.PitchTier')[[1]][1]
}))[,1]

# Put all the reference textgrids into a list
ref_tgs <- lapply(pt_filenames, function(elt) {
  phrase<-str_split(elt, '.PitchTier')[[1]][1]
  tg.read(paste0(path, "_textgrid/", paste0(phrase, '_auto.TextGrid')))
})

# Put all the reference pitch tiers into a list
ref_pts_interp <- lapply(pt_filenames, function(elt) {
  my_pt<-pt.read(paste0(path, "_pitchtier/", elt))
  interpolated <- pt.interpolate(my_pt, seq(0, my_pt$tmax, by=0.01))
  interpolated$f <- hertz_to_semitones(interpolated$f, ref_freq)
  interpolated$f <- interpolated$f-mean(interpolated$f)
  interpolated
})

# Put all the Prosogram pitch tiers into a list
ref_psgs_interp <- lapply(psg_filenames, function(elt) {
  my_pt<-pt.read(paste0(path, "_prosogram_pt/", elt))
  interpolated <- pt.interpolate(my_pt, seq(0, my_pt$tmax, by=0.01))
  interpolated$f <- hertz_to_semitones(interpolated$f,ref_freq)
  interpolated$f <- interpolated$f-mean(interpolated$f)
  interpolated
})

# Put all the reference intensity tiers into a list
ref_its_interp <- lapply(it_filenames, function(elt) {
  my_it <- it.read(paste0(path, "_intensity/", elt))
  it.interpolate(my_it, seq(0, my_it$tmax, by=0.01))
})

# Get the times of each phrase
ref_times <- do.call("rbind", lapply(ref_pts_interp, function(elt) {
  elt$tmax
}))[,1]

# A tibble containing each phrase and its duration
ref_info <- tibble(phrase=ref_phrases, duration=ref_times)

```

Some helper functions
```{r}
# Get the TextGrid
get_ref_tg <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_tgs[[index]])
}

# Gets the interpolated prosogram object
get_ref_psgs_interp <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_psgs_interp[[index]])
}

# Gets interpolated pitchtier for reference
get_ref_pts_interp <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_pts_interp[[index]])
}

# A function that gets the duration given the phrase name
get_ref_duration <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_info$duration[index])
}

# Get the times stamps for interpolation given the phrase name
get_ref_timestamps <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_pts_interp[[index]]$t)
}

# Get the interpolated frequency values given the phrase name
# (frequency time series)
get_ref_tsf <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_pts_interp[[index]]$f)
}

# Get the interpolated prosogram frequency values given the phrase name
# (prosogram frequency time series)
get_ref_ptsf <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_psgs_interp[[index]]$f)
}

# Get the interpolated intensity values given the phrase name
# (intensity time series)
get_ref_tsi <-function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_its_interp[[index]]$i)
}
```


# 2. Gestures 
```{r}

library("jsonlite")
library("timetk")

# Get all the filenames of the gestures
path="../data/21_02-study/all_gestures/"
setwd(path)
gest_filenames <- dir(pattern="\\.gest$")
name <- gest_filenames[1]

# Extract the reference phrase from the whole gesture name
get_ref_name <- function(gest_name) {
  return(str_split(gest_name, '-')[[1]][3])
}

# Finds the number of samples in the reference for the particular gesture
get_num_samples <-function(gest_name) {
# Find how many samples are in the ref file
  ref_phrase <- get_ref_name(gest_name)  
  return(length(get_ref_timestamps(ref_phrase)))
}

# Load gest data and convert time
prep_gest<-function(gest) {
  min_scrub <- gest$scrub[1]
  max_scrub <- tail(gest$scrub, 1)
    
  # Convert time to percentage
  max_time <- tail(gest$t_end, 1)
  gest <- gest %>% mutate(percent=t_init/max_time) %>%
             # Add another column for percent scaled to the scrub start and end values
             mutate(percent_scaled = rescale(percent, to=c(min_scrub, max_scrub), from=c(0, 1)))  %>%
             # only keep the columns we need
             select(percent, f, scrub, percent_scaled)
  
  return(gest)
}


# args: data - tibble with columns: percent (% of way through signal) & f (frequency at that point), 
# num_samples - # equally spaced points in outpt
# returns: tibble with coluumns index & value. index has num_samples equally spaced points from 0 to 1
# values are interplolated from f
get_interpolated_data <- function(data, num_samples) {
  # Add end points at 0 and 1 if they don't already exist, duplicating first and last available f value
  if (! 0 %in% data$percent) {
    data <- add_row(data, percent=0, f=data$f[1], scrub=data$scrub[1], .before=1)
  }
  if (! (1 %in% data$percent)) {
    data <- add_row(data, percent=1, f=tail(data$f, 1), scrub=tail(data$scrub, 1))
  }
          
  # Create a tibble with all the points we are interested in, with NA values
  sample_points <- tibble(percent=seq(0, 1, length.out=num_samples), f=NA, scrub=NA) 
  
  # Add all the sample points whose percent value doesn't already exist in data
  data2 <- bind_rows(data, filter(sample_points, !(percent %in% data$percent)))  %>%
    # Then sort by scrub columns  
    arrange(percent)
  
  # Transform into zoo object to fill the NAs with interpolated values
  z <- read.zoo(data2) %>% na.approx %>%
   tk_tbl(preserve_index=TRUE, rename_index="index") %>%
   filter(index %in% sample_points$percent)
  
  return(z)
}

# args: data - tibble with columns: scrub (% of way through REFERENCE signal), 
# f (frequency of ORIGINAL signal at that point), 
# num_samples - # equally spaced points in outpt
# returns: tibble with coluumns index & value. index has num_samples equally spaced points from the start and end of scrub, f is interpolated
get_interpolated_data_scrub <- function(data, num_samples) {
  # Get the starting and ending scrub values
  start_scrub <- data$scrub[1]
  end_scrub <- tail(data$scrub, 1)
  
  # Remove rows with duplicated scrub values
  data<-data[!duplicated(data$scrub),]
  
  # Create tibble with all the points we are interested in
  sample_points <- tibble(scrub=seq(start_scrub, end_scrub, length.out = num_samples), f=NA, percent=NA)
  
  # # Add all the sample points whose scrub value doesn't alread exist to data
  data2 <- bind_rows(data, filter(sample_points, !(scrub %in% data$scrub))) %>%
    # Then sort by scrub columns
    arrange(scrub) %>% select(scrub, f, percent)

  # # Transform into zoo object to fill the NAs with interpolated values
  z <- read.zoo(data2) %>% na.approx %>%
   tk_tbl(preserve_index=TRUE, rename_index="index") %>%
   filter(index %in% sample_points$scrub)
   
  return(z)
}

setwd("../../../notebooks/")

# A vector with just the names of the phrases (w/o .json extension)
gests <- do.call("rbind", lapply(gest_filenames, function(elt) {
  str_split(elt, '.gest')[[1]][1]
}))[,1]

# Original gestures
gest_originals <- lapply(gest_filenames, function(elt) {
  result <- fromJSON(paste0(path, elt)) %>% as_tibble() %>% 
  # NOTE THIS EXTRA STEP      
  prep_gest()
})

# Returns the index of the gesture
get_gest_index <- function(gest_name) {
  index <- match(gest_name, gests)
  if (is.na(index)) { return(NULL) }
  return(index)
}

# Interpolated time series data of f & scrub value
gest_interps <- lapply(gests, function(elt) {
  # Elt is the name of a gesture. We want to find its index first
  index<-get_gest_index(elt)
  
  # In order to get the actual gesture data
  gest_orig<-gest_originals[[index]]
  
  # Gets number of samples for the gest, which is computed from the reference
  num_samples<-get_num_samples(elt)
  
  # Do the interpolation  
  gest_interp<-get_interpolated_data(gest_orig, num_samples)
  
  return(gest_interp)
})

# Organize gestures into a Tibble
gests_data <- do.call("rbind", lapply(gests, function(elt) {
  parts<-str_split(elt, '-')[[1]]
  ref_phrase <- parts[3]
  phrase_id <- str_split(ref_phrase, '_')[[1]][1]
  tibble(phrase=ref_phrase, pid=phrase_id, type=parts[2], subject=parts[4], order=parts[1], gest_name=elt)
})) %>% mutate(id = row_number()) %>%
  select(subject, type, pid, order,gest_name, phrase, id)
```

## Comparison

### 1. Weighted correlation of pitch and timing
```{r}
get_gest_comparison_data <- function(gest_id) {
  # Get the gesture from the list by ID
  my_gest <- slice(gests_data, gest_id)  
  
  # Get the original data 
  my_gest_data <- gest_originals[[gest_id]]
  # Find the starting and ending scrub times
  start_scrub <- my_gest_data$scrub[1]
  end_scrub <- tail(my_gest_data$scrub, 1)

  # Find the corresponding phrase for this gesture
  my_ref <- get_ref_pts_interp(my_gest$phrase)
  # Number of points in my_ref
  my_ref_length <- length(my_ref$f)
  # Get the start and index of the reference phrase based on the start and end scrub points
  my_ref_start_index <- floor(start_scrub * my_ref_length)
  my_ref_end_index <- ceiling(end_scrub * my_ref_length)
  # Get the part of the reference to compare with the gesture
  my_ref_f <- my_ref$f[my_ref_start_index:my_ref_end_index]
  my_ref_t <- my_ref$t[my_ref_start_index:my_ref_end_index]
  
  # Get the intensity too
  my_ref_i <- get_ref_tsi(my_gest$phrase)[my_ref_start_index:my_ref_end_index]
  # Also get the prosogram f0 stylization for the reference
  my_ref_f_psg <- get_ref_psgs_interp(my_gest$phrase)$f[my_ref_start_index:my_ref_end_index]
  
  # Now, interpolate the original gesture based on the number of points in the subset of the reference
  my_gest_interp<-get_interpolated_data(my_gest_data, length(my_ref_f))
  
  # Put everything into a tibble
  data_to_compare <- tibble(subject=my_gest$subject, phrase=my_gest$phrase, condition=my_gest$type,
                            percent_t = seq(0, 1, length.out = length(my_ref_f)), 
                            gest_scrub = my_gest_interp$scrub, gest_f = my_gest_interp$f, 
                            ref_t = my_ref_t, ref_f = my_ref_f, ref_f_psg = my_ref_f_psg, ref_i = my_ref_i)
  return(data_to_compare)
}

gest_comparison_data <- lapply(gests_data$id, get_gest_comparison_data)
gest_comparison_data_tibble <- bind_rows(gest_comparison_data)  

```



```{r}
compare2 <- function(gest_id) {
  # Get the gesture from the list by ID
  my_gest <- slice(gests_data, gest_id)  
  
  # Get the original data 
  my_gest_data <- gest_originals[[gest_id]]
  # Find the starting and ending scrub times
  start_scrub <- my_gest_data$scrub[1]
  end_scrub <- tail(my_gest_data$scrub, 1)

  # Find the corresponding phrase for this gesture
  my_ref <- get_ref_psgs_interp(my_gest$phrase)
  # Number of points in my_ref
  my_ref_length <- length(my_ref$f)
  # Get the start and index of the reference phrase based on the start and end scrub points
  my_ref_start_index <- floor(start_scrub * my_ref_length)
  my_ref_end_index <- ceiling(end_scrub * my_ref_length)
  # Get the part of the reference to compare with the gesture
  my_ref_f <- my_ref$f[my_ref_start_index:my_ref_end_index]
  my_ref_t <- my_ref$t[my_ref_start_index:my_ref_end_index]
  
  # Get the intensity too
  my_ref_i <- get_ref_tsi(my_gest$phrase)[my_ref_start_index:my_ref_end_index]
  
  # Now, interpolate the original gesture based on the number of points in the subset of the reference
  my_gest_interp<-get_interpolated_data(my_gest_data, length(my_ref_f))

  
  return(weightedCorr(my_ref_f, my_gest_interp$f, method = "Pearson", 
                      weights = my_ref_i, ML = FALSE, fast = TRUE))
}

# Run new comparison on all the gestures
compare2_all <- do.call("rbind", lapply(gests_data$id, function(elt) {
  compare2(elt)
}))[,1]

gests_data <- add_column(gests_data, wcorr2 = compare2_all)
```

### 2. Correlation of pitch, disregarding timing of gesture

```{r}
compare3 <- function(gest_id) {
  # Get the gesture from the list based on id
  my_gest <- slice(gests_data, gest_id)  
  
  # Get the original data 
  my_gest_data <- gest_originals[[gest_id]]
  # Find the starting and ending scrub times
  start_scrub <- my_gest_data$scrub[1]
  end_scrub <- tail(my_gest_data$scrub, 1)
  
  # Find the corresponding phrase for this gesture
  my_ref <- get_ref_psgs_interp(my_gest$phrase)
  # Number of points in my_ref
  my_ref_length <- length(my_ref$f)
  # Get the start and index of the reference phrase based on the start and end scrub points
  my_ref_start_index <- floor(start_scrub * my_ref_length)
  my_ref_end_index <- ceiling(end_scrub * my_ref_length)
  # Get the part of the reference to compare with the gesture
  my_ref_f <- my_ref$f[my_ref_start_index:my_ref_end_index]
  my_ref_t <- my_ref$t[my_ref_start_index:my_ref_end_index]
  
  # Get the intensity too
  my_ref_i <- get_ref_tsi(my_gest$phrase)[my_ref_start_index:my_ref_end_index]
  
  # Now, interpolate the original gesture based on the number of points in the subset of the reference
  my_gest_interp<-get_interpolated_data_scrub(my_gest_data, length(my_ref_f))
  
  return(weightedCorr(my_ref_f, my_gest_interp$f, method = "Pearson", 
                      weights = my_ref_i, ML = FALSE, fast = TRUE))
}

# Run new comparison on all the gestures
compare3_all <- do.call("rbind", lapply(gests_data$id, function(elt) {
  compare3(elt)
}))[,1]

gests_data <- add_column(gests_data, wcorr3 = compare3_all)

```


### 3. RMSE
```{r}
library("mltools")

get_rmse <- function(gest_id) {
  # Get the gesture from the list based on id
  my_gest <- slice(gests_data, gest_id)  
  
  # Get the original data 
  my_gest_data <- gest_originals[[gest_id]]
  # Find the starting and ending scrub times
  start_scrub <- my_gest_data$scrub[1]
  end_scrub <- tail(my_gest_data$scrub, 1)
  
  # Find the corresponding phrase for this gesture
  my_ref <- get_ref_psgs_interp(my_gest$phrase)
  # Number of points in my_ref
  my_ref_length <- length(my_ref$f)
  # Get the start and index of the reference phrase based on the start and end scrub points
  my_ref_start_index <- floor(start_scrub * my_ref_length)
  my_ref_end_index <- ceiling(end_scrub * my_ref_length)
  # Get the part of the reference to compare with the gesture
  my_ref_f <- my_ref$f[my_ref_start_index:my_ref_end_index]
  my_ref_t <- my_ref$t[my_ref_start_index:my_ref_end_index]
  
  # Get the intensity too
  my_ref_i <- get_ref_tsi(my_gest$phrase)[my_ref_start_index:my_ref_end_index]
  
  # Now, interpolate the original gesture based on the number of points in the subset of the reference
  my_gest_interp<-get_interpolated_data_scrub(my_gest_data, length(my_ref_f))
  
  return(rmse(preds=my_ref_f, actuals=my_gest_interp$f,
                      weights = my_ref_i))
}

# Run new comparison on all the gestures
rmse_all <- do.call("rbind", lapply(gests_data$id, function(elt) {
  get_rmse(elt)
}))[,1]

gests_data <- add_column(gests_data, rmse = rmse_all)

```


# Plots
By phrase
```{r}
gests_data %>%
  mutate(pid = fct_relevel(pid, 
            "2", "2bis", "7", 
            "7bis", "8", "8bis", 
            "10", "10bis", "11", "11bis", "21", "21bis")) %>%
  ggplot(aes(x=pid, y=wcorr2, fill=factor(type))) +
  geom_boxplot() +
  labs(title="Correlation of gesture with reference", 
            subtitle="Grouped by phrase",
            x="Phrase id", y="Correlation")
```

```{r}
gests_data %>%
  mutate(pid = fct_relevel(pid, 
            "2", "2bis", "7", 
            "7bis", "8", "8bis", 
            "10", "10bis", "11", "11bis", "21", "21bis")) %>%
  ggplot(aes(x=pid, y=rmse, fill=factor(type))) +
  geom_boxplot() +
  labs(title="RMSE of gesture with reference", 
            subtitle="Grouped by phrase",
            x="Phrase id", y="RMSE")
```

By subject
```{r}
# Boxplots of wcorr by subject
gests_data %>%
  ggplot(aes(x=subject, y=wcorr2, fill=factor(type))) +
  geom_boxplot() +
  labs(title="Correlation of gesture with reference", 
            subtitle="Grouped by subject",
            x="Subject id", y="Correlation score")

```


### Subject info

```{r}
# Load subject info into a tibble
path="../data/21_02-study/"
setwd(path)
subjects <- read.table(file = 'subjects.tsv', sep = '\t', header = TRUE) %>% tibble()
```

# Basic Subject Information
```{r}
mean(subjects$age)
sd(subjects$age)
```


## Some filters for subjects
```{r}
require(gridExtra)

# Native speakers
natives <- subjects %>% filter(lvl_french == "N")

learners_gests <- gests_data %>% filter(!(subject %in% natives$id)) %>%
  ggplot(aes(x=subject, y=wcorr2, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) + 
  labs(title="Correlation of f0 curves with timing", subtitle="Non-native", y="Correlation")

natives_gests <- gests_data %>% filter(subject %in% natives$id) %>%
  ggplot(aes(x=subject, y=wcorr2, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) +
  labs(title="", subtitle="Native", y="Correlation")


grid.arrange(learners_gests, natives_gests, ncol=2)

```

```{r}
# Native speakers
natives <- subjects %>% filter(lvl_french == "N")

learners_gests <- gests_data %>% filter(!(subject %in% natives$id)) %>%
  ggplot(aes(x=type, y=wcorr2, fill=type)) +
  geom_boxplot(show.legend = FALSE) + 
  labs(title="Correlation of f0 curves with timing", subtitle="Non-native", y="Correlation")

natives_gests <- gests_data %>% filter(subject %in% natives$id) %>%
  ggplot(aes(x=type, y=wcorr2, fill=type)) +
  geom_boxplot(show.legend = FALSE) +
  labs(title="", subtitle="Native", y="Correlation")


grid.arrange(learners_gests, natives_gests, ncol=2)

```

```{r}
# Native speakers
natives <- subjects %>% filter(lvl_french == "N")

learners_gests <- gests_data %>% filter(!(subject %in% natives$id)) %>%
  ggplot(aes(x=type, y=rmse, fill=type)) +
  geom_boxplot(show.legend = FALSE) + 
  labs(title="RMSE of f0 curves with timing", subtitle="Non-native", y="Correlation")

natives_gests <- gests_data %>% filter(subject %in% natives$id) %>%
  ggplot(aes(x=type, y=rmse, fill=type)) +
  geom_boxplot(show.legend = FALSE) +
  labs(title="", subtitle="Native", y="Correlation")


grid.arrange(learners_gests, natives_gests, ncol=2)

```

```{r}

# Musicians
musicians <- subjects %>% filter(music == "Y")

nonmus_gests <- gests_data %>% filter(!(subject %in% musicians$id)) %>%
  ggplot(aes(x=type, y=wcorr2, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) + 
  labs(title="Correlation of f0 curves with timing", subtitle="Non-musician", y="Correlation")

musician_gests <- gests_data %>% filter(subject %in% musicians$id) %>%
  ggplot(aes(x=type, y=wcorr2, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) +
  labs(title="", subtitle="Musician", y="Correlation")

grid.arrange(nonmus_gests, musician_gests, ncol=2)

```

```{r}

# Musicians
musicians <- subjects %>% filter(music == "Y")

nonmus_gests <- gests_data %>% filter(!(subject %in% musicians$id)) %>%
  ggplot(aes(x=type, y=rmse, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) + 
  labs(title="RMSE f0 curves with timing", subtitle="Non-musician", y="Correlation")

musician_gests <- gests_data %>% filter(subject %in% musicians$id) %>%
  ggplot(aes(x=type, y=rmse, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) +
  labs(title="", subtitle="Musician", y="Correlation")

grid.arrange(nonmus_gests, musician_gests, ncol=2)

```

```{r}
# Musicians
musicians <- subjects %>% filter(music == "Y")

nonmus_gests <- gests_data %>% filter(!(subject %in% musicians$id)) %>%
  ggplot(aes(x=subject, y=wcorr2, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) + 
  labs(title="Correlation of f0 curves with timing", subtitle="Non-musician", y="Correlation")

musician_gests <- gests_data %>% filter(subject %in% musicians$id) %>%
  ggplot(aes(x=subject, y=wcorr2, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) +
  labs(title="", subtitle="Musician", y="Correlation")

grid.arrange(nonmus_gests, musician_gests, ncol=2)

```

## F0 only, timing not considered

```{r}
# Native speakers
natives <- subjects %>% filter(lvl_french == "N")

learners_gests <- gests_data %>% filter(!(subject %in% natives$id)) %>%
  ggplot(aes(x=subject, y=wcorr3, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) + 
  labs(title="Correlation of f0 only", subtitle="Non-native", y="Correlation")

natives_gests <- gests_data %>% filter(subject %in% natives$id) %>%
  ggplot(aes(x=subject, y=wcorr3, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) +
  labs(title="", subtitle="Native", y="Correlation")


grid.arrange(learners_gests, natives_gests, ncol=2)
```

```{r}
# Musicians
musicians <- subjects %>% filter(music == "Y")

nonmus_gests <- gests_data %>% filter(!(subject %in% musicians$id)) %>%
  ggplot(aes(x=subject, y=wcorr3, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) + 
  labs(title="Correlation of f0 only", subtitle="Non-musician", y="Correlation")

musician_gests <- gests_data %>% filter(subject %in% musicians$id) %>%
  ggplot(aes(x=subject, y=wcorr3, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) +
  labs(title="", subtitle="Musician", y="Correlation")

grid.arrange(nonmus_gests, musician_gests, ncol=2)

```

## RMSE plots

```{r}
# Native speakers
natives <- subjects %>% filter(lvl_french == "N")

learners_gests <- gests_data %>% filter(!(subject %in% natives$id)) %>%
  ggplot(aes(x=subject, y=rmse, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) + 
  labs(title="RMSE of f0 curves with timing", subtitle="Non-native", y="RMSE")

natives_gests <- gests_data %>% filter(subject %in% natives$id) %>%
  ggplot(aes(x=subject, y=rmse, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) +
  labs(title="", subtitle="Native", y="RMSE")


grid.arrange(learners_gests, natives_gests, ncol=2)
```

```{r}
# Musicians
musicians <- subjects %>% filter(music == "Y")

nonmus_gests <- gests_data %>% filter(!(subject %in% musicians$id)) %>%
  ggplot(aes(x=subject, y=rmse, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) + 
  labs(title="RMSE of f0 curves with timing", subtitle="Non-musician", y="RMSE")

musician_gests <- gests_data %>% filter(subject %in% musicians$id) %>%
  ggplot(aes(x=subject, y=rmse, fill=factor(type))) +
  geom_boxplot(show.legend = FALSE) +
  labs(title="", subtitle="Musician", y="RMSE")

grid.arrange(nonmus_gests, musician_gests, ncol=2)

```

# Plot reference + attempts

Timing of gesture

```{r}
# Plot gesture with its attempts
plot_ref_with_gestures <- function(phrase_id, my_type='guide') {
  my_ref <- get_ref_psgs_interp(ref_phrases[[phrase_id]])
  ref_data <- tibble(percent=my_ref$t/my_ref$tmax, f=my_ref$f)

  # Get all the gestures for this reference
  my_ref_phrase <- ref_phrases[phrase_id]
  my_gestures <- gests_data %>% filter(phrase == my_ref_phrase, type == my_type)

  # Iterate through the ids, combine all gesture data into a giant tibble
  selected_gests<-do.call("rbind", lapply(my_gestures$id, function(elt) {
    # Get the subject for the gesture
    my_subject <- slice(gests_data, elt)$subject
  
    # Get the data
    my_gest_data <- gest_originals[[elt]] %>% mutate(subject=my_subject)
    return(my_gest_data)
  }))

 ggplot(data=ref_data, aes(x=percent, y=f, color="Reference")) +
            scale_color_discrete(name = "Data source") +
            geom_line(size=2) + 
            geom_line(data=selected_gests, mapping=aes(x=percent_scaled, y=f, color=subject)) +
            labs(title=paste0("Reference and gesture - ", my_type),
                 subtitle=paste0("Phrase:", my_ref_phrase), y="Frequency (Semitones)", x="Percent time")
 
}

```

Ignoring timing of gesture
```{r}
plot_ref_with_gestures_notiming <- function(phrase_id, my_type='guide') {
  my_ref <- get_ref_psgs_interp(ref_phrases[[phrase_id]])
  ref_data <- tibble(percent=my_ref$t/my_ref$tmax, f=my_ref$f)

  # Get all the gestures for this reference
  my_ref_phrase <- ref_phrases[phrase_id]
  my_gestures <- gests_data %>% filter(phrase == my_ref_phrase, type == my_type)

  # Iterate through the ids, combine all gesture data into a gant tibble
  selected_gests<-do.call("rbind", lapply(my_gestures$id, function(elt) {
    # Get the subject for the gesture
    my_subject <- slice(gests_data, elt)$subject
  
    # Get the data
    my_gest_data <- gest_originals[[elt]] %>% mutate(subject=my_subject)
    return(my_gest_data)
  }))

 ggplot(data=ref_data, aes(x=percent, y=f, color="Reference")) +
            scale_color_discrete(name = "Data source") +
            geom_line(size=2) + 
            geom_line(data=selected_gests, mapping=aes(x=scrub, y=f, color=subject)) +
            labs(title=paste0("Reference and gesture - ", my_type),
                 subtitle=paste0("Phrase:", my_ref_phrase), y="Frequency (Semitones)", x="Percent time")
 
}

```

Plotting only timing
```{r}
plot_ref_with_gestures_timing_only <- function(phrase_id, my_type='guide') {
  my_ref <- get_ref_psgs_interp(ref_phrases[[phrase_id]])
  ref_data <- tibble(percent=my_ref$t/my_ref$tmax, f=my_ref$f)

  # Get all the gestures for this reference
  my_ref_phrase <- ref_phrases[phrase_id]
  my_gestures <- gests_data %>% filter(phrase == my_ref_phrase, type == my_type)

  # Iterate through the ids, combine all gesture data into a gant tibble
  selected_gests<-do.call("rbind", lapply(my_gestures$id, function(elt) {
    # Get the subject for the gesture
    my_subject <- slice(gests_data, elt)$subject
  
    # Get the data
    my_gest_data <- gest_originals[[elt]] %>% mutate(subject=my_subject)
    return(my_gest_data)
  }))

 ggplot(data=ref_data, aes(x=percent, y=percent, color="Reference")) +
            scale_color_discrete(name = "Data source") +
            geom_line(size=2) + 
            geom_line(data=selected_gests, mapping=aes(x=percent_scaled, y=scrub, color=subject)) +
            labs(title=paste0("Reference and gesture - ", my_type),
                 subtitle=paste0("Phrase:", my_ref_phrase), y="Scrub percentage", x="Percent time")
 
}
```

