---
title: "BRMS Practice"
output: html_notebook
---

Exercises in Chapter 11 of Statistical Rethinking, using 

A. Solomon Kurz's [Statistical Rethinking Recoded](https://bookdown.org/ajkurz/Statistical_Rethinking_recoded/), which translates the examples of the book into BRMS.

```{r}
# Load usual libraries
library(tidyverse)
```

## Binomial Logistic Regression with Chimpanzees

```{r}
# Get the data from the Rethinking library
library(rethinking)
data(chimpanzees)
d <- chimpanzees

# Detach rethinking, because it conflicts with brms. Then load brms.
detach(package:rethinking, unload = T)
library(brms)
rm(chimpanzees)
```

Start with the simplest intercept-only model. Intercept is the average value of $pulled\_left$ without any predictors.

$$ pulled\_left_i \sim\ Binomial(1, p_i) \\
  logit(p_i) = \alpha \\
  \alpha \sim\ Normal(0, 10) 
$$

```{r}
b10.1 <-
  brm(data = d, family = binomial,
      pulled_left | trials(1) ~ 1,
      prior(normal(0, 10), class = Intercept),
      seed = 10)

# Summary of intercept
fixef(b10.1) %>%
  round(digits = 2)
```

We want to convert parameters the outcome scale using the inverse link function. Our link function is the logit function, so we use the logistic function (a.k.a. inv_logit) 

```{r}
fixef(b10.1) %>%
  inv_logit_scaled()
```

Model 2 - Add a $\beta$ parameter (slope) for the treatmeant of $prosoc\_left$. Give a vaguely informative prior.

Model 3 - Full model

```{r}
b10.2 <-
  brm(data = d, family = binomial,
      pulled_left | trials(1) ~ 1 + prosoc_left,
      prior = c(prior(normal(0, 10), class = Intercept),
                prior(normal(0, 10), class = b)),
      seed = 10)

b10.3 <-
  update(b10.2,
         newdata = d,
         formula = pulled_left | trials(1) ~ 1 + prosoc_left + condition:prosoc_left)
```

Compute WAIC for each model and save the result in the brmfit objects returned by brm:
```{r}
b10.1 <- add_criterion(b10.1, "waic")
b10.2 <- add_criterion(b10.2, "waic")
b10.3 <- add_criterion(b10.3, "waic")
```

Comparing:

```{r}
w <- loo_compare(b10.1, b10.2, b10.3, criterion = "waic")
print(w, simplify = F)
```

To get differences from elpd metric to WAIC metric:
```{r}
cbind(waic_diff = w[, 1] * -2,
      se        = w[, 2] *  2) %>% 
  round(digits = 2)
```

Plot WAICs

```{r}
w %>%
  data.frame() %>% 
  rownames_to_column(var = "model") %>% 
  
  ggplot() +
  geom_pointrange(aes(x = reorder(model, -waic), y = waic,
                      ymin = waic - se_waic,
                      ymax = waic + se_waic,
                      color = model),
                  shape = 16) +
  coord_flip() +
  labs(x = NULL, y = NULL,
       title = "WAIC") +
  theme(axis.ticks.y    = element_blank(),
        legend.position = "none")
```




